Agile Inter-team Software Development

### 2019-01-21 Draft/Parts/Conclusion.tex
Finish pass on introduction.

\section{Conclusion}\label{sec:conclusion}
As we have seen, inter-team communication can be an obstacle in agile teams working on the same thing as intermediaries in communication and lack of common personal causes things to go haywire if left unchecked.
To reduce this problem a number of small additions can be done to the process as specified but the most important part of the change is a good architecture and design which is available to all the teams and thus provides a common framework to all the teams involved.

>>>>

\section{Conclusion}\label{sec:conclusion}
As we have seen, inter-team communication can be an obstacle in agile teams working together, as intermediaries in communication and lack of personal communication causes a distruption in software process.
To reduce this problem a number of small additions can be done to the process as specified but the most important part of the change is a good architecture and design which is available to all the teams and thus provides a common framework to all the teams involved.

### 2019-01-21 Draft/Parts/Introduction.tex
Finish pass on introduction.

As mentioned in the Agile Manifesto \cite{beck2001agile}, Individuals and Interactions are given more value than the processes and tools. At the same time, an agile team is supposed to contain all that is required for them to do their work, thus interactions no matter how valuable usually are done intra-team only. Thus, when a situation arrives where two or more agile teams need to work together to achieve a common goal the usual approach taken by companies fail. The agile approach of interacting in-person fails due to a few reasons such as the vertical structure of the company organization and the existence of middle managers \cite{dzone_article}. This large number of intermediaries in inter team communication causes the process to crumble and fall apart as it takes longer than usual time for messages to reach their destination then what agile can afford.
This problem is harder to fix as this is so embedded in the working culture of the current organizations that changing them will take a long time, thus an immediate patch that works is required. And that’s where the approaches listed in the article comes in. We have collected a couple of approaches which if implemented efficiently results in a more stable and functioning agile process model. Thus, in the following sections we will be explaining couple of approaches we came across.
\linebreak
\linebreak
In Section ~\ref{sec:proc_impv}, we will be explaining the improvements that can be made to the process and team structures to get better collaboration out of the team involved.
\linebreak
\linebreak
In Section ~\ref{sec:tech_impv}, we will be explaining the enhancements that can be done in the technology stack being used and in the different ways in which technology can help in improving the process.

>>>>

%Introduction (Introducing the topic)

%AM: What is the problem?
%introduce the need to scale to multiple agile teams
Agile approaches are popular in software development for numerous reasons.
However, the structure of the agile process does not lend itself to large teams and is not suitable for large projects.
With the growth in complex software, situations arise where multiple agile teams need to work together to achieve a common goal.
%thesis statement
When scaling to parallel agile teams, the most important consideration is quality communication, both personal and architectural.
%
For an example of a company developing a complex piece of software, consider Spotify AB who has over 30 teams \cite{kniberg12}.
Spotify is a streaming music client which supports media, commercial, and social features.
The basic element of development organization at Spotify is the Squad, analogous to a Scrum team.
%Each Squad is the autonomous developer, with a localized working area, of a particular sub-system in the product.
Squads in related areas are grouped together into Tribes. 
The overall structure is illustrated in Figure~\ref{fig:spotify_structure}.
\begin{figure}[h]
  \includegraphics[width=\linewidth]{images/kniberg12_structure.png}
  \caption{Agile team organization at Spotify \cite{kniberg12}.}
  \label{fig:spotify_structure}
\end{figure}

%AM: Why is it interesting/important?
%introduce agile
As outlined in the Agile Manifesto \cite{beck2001agile}, an agile process gives individuals and interactions value over processes and tools.
An agile team should contain all that is required for them to do their work, thus interactions are intensely intra-team.
However, diverse feature sets such as required in the Spotify application necessitate many skillsets and substantial manpower.
By moving to a multi-team model, complex projects can benefit from agility, provided that the process is adapted.
%personal communication
Multiple teams increases the importance of communication, from simple interpersonal communication to system specification. 
The agile approach of interacting in-person can fail due to reasons such as the vertical structure of the company organization and layers of middle managers \cite{dzone_article}.
The large number of intermediaries can cause an agile process to breakdown as it takes longer than usual time for messages to reach their destination than can afforded.
%arch communication
In an agile process, where Big Design Up-front may typically be avoided, the move to multiple teams motivates a need to communicate design decisions.
%todo: component boundaries?
For successful integration of technological components, system elements must have well defined functional specifications, and interfaces.

%RA: feel like we can skip AM suggest section on Why is it hard.
%AM: What are the key components of [the] proposed approach? Also include assumptions/limitations
%We discuss approaches, which if implemented correctly, provide a more robust and functional process for inter-team agile development.

%outline of rest of paper
This document is organized as follows: Introduction, Communication Concerns, Supporting Communication in Inter-team Development, and Conclusion. 
In Section ~\ref{sec:spt_ex}, we discuss example communication concerns in an agile project.
In Section ~\ref{sec:prop_appro}, we present some process adaptations that can help to resolve issues.
Lastly, Section ~\ref{sec:conclusion} concludes with an overview of important aspects of inter-team agile development.

%This problem is difficult to fix as this is so embedded in the working agile culture of the current organizations that changing them will take a long time, thus an immediate patch that works is required. %RA: this is an important observation, just too detailed for intro.

### 2019-01-21 Draft/Parts/Main.tex
Finish pass on introduction.

\section{Spotify: A Canonical Example} 
\label{sec:spt_ex} 
For an example of a company using many agile teams, consider Spotify who has over 30 teams \cite{kniberg12}.
The basic element of development organization at Spotify is the Squad, analogous to a Scrum team.
Each Squad is the autonomous developer, with a localized working area, of a particular sub-system in the product.
Squads in related areas are grouped together into Tribes. 
The overall structure is illustrated in Figure~\ref{fig:spotify_structure}.
Although larger than Squads (7-10 members), Tribes are limited in size (< 100) to ensure smooth communication.

\begin{figure}[h]
  \includegraphics[width=\linewidth]{images/kniberg12_structure.png}
  \caption{Agile team organization at Spotify \cite{kniberg12}.}
  \label{fig:spotify_structure}
\end{figure}

\subsection{Communication at Spotify}
%social fixes
A fundamental issue with tasking teams with different goals is that teams can become isolated with respect to the context of their work.
At Spotify \cite{kniberg12}, offices are laid out so that the Squads making up a Tribe are spatially close. This leads to an environment where an informal exchange of information on the Tribes work will occur.
%second problem
Consider another scenario: a tester on a particular agile team invests time to solve a particular problem, which is also faced by another tester on a different team. Without communication, these team members would perform redundant work.
To address this problem Spotify defines Chapters \cite{kniberg12}, which are crosscutting divisions which gathers individuals with similar roles across different Squads.

\section{Communication in Inter-team Development}
\label{sec:prop_appro} 
The general problem of communication can be tackled from two perspectives.
First, stakeholders at different levels need to have ways to pass information.
This can be addressed by adaptions in development process and leveraging technology.
Second, the quality of communication needs to be accurate.
This can be addressed by sound system specification through architecture and design.
%In Section ~\ref{sec:proc_impv}, we discuss the adaptations to an agile process, and team structure, to support better collaboration between teams.
%In Section ~\ref{sec:tech_impv}, we discuss the ways in which technology improve inter-team communication
%In Section ~\ref{sec:imp_of_dsgn}, we discuss the role of architecture and design in mitigating communication issues.

\subsection{Process Improvements} 
\label{sec:proc_impv}
	There are many small changes \cite{collabAcrossAgile_article} that we can incorporate in our process model to make sure that parallel developing agile teams do not run into problems when they reach the integration phase.
	These changes are to be made part of the entire process and are not to be implemented only in the end.

>>>>

\section{Communication Concerns}\label{sec:spt_ex} 
Although larger than Squads (7-10 members), Tribes are limited in size (< 100) to ensure smooth communication.
%social fixes
A fundamental issue with tasking teams with different goals is that teams can become isolated with respect to the context of their work.
At Spotify \cite{kniberg12}, offices are laid out so that the Squads making up a Tribe are spatially close. This leads to an environment where an informal exchange of information on the Tribes work will occur.
%second problem
Consider another scenario: a tester on a particular agile team invests time to solve a particular problem, which is also faced by another tester on a different team. Without communication, these team members would perform redundant work.
To address this problem Spotify defines Chapters, which are crosscutting divisions which gathers individuals with similar roles across different Squads  \cite{kniberg12}.

\section{Supporting Communication in Inter-team Development}
\label{sec:prop_appro} 
The general problem of communication can be tackled from two perspectives.
First, stakeholders at different levels need to have ways to pass information.
This can be addressed by adaptions in development process and leveraging technology.
Second, the quality of communication needs to be accurate.
This can be addressed by sound system specification through architecture and design.
%In Section ~\ref{sec:proc_impv}, we discuss the adaptations to an agile process, and team structure, to support better collaboration between teams.
%In Section ~\ref{sec:tech_impv}, we discuss the ways in which technology improve inter-team communication
%In Section ~\ref{sec:imp_of_dsgn}, we discuss the role of architecture and design in mitigating communication issues.

\subsection{Process Improvements} 
\label{sec:proc_impv}
	There are many small changes \cite{collabAcrossAgile_article} that we can incorporate in our process model to make sure that parallel developing agile teams do not run into problems when they reach the integration phase.
	These changes are to be made part of the entire process.
